ms_results

### 2024-02-29 ms_results.Rmd

```{r load_data}
# Directory
datadir <- "outputs"

@@

![Figure 1: Increases in global export of aquatic foods. a) Exports of global marine and freshwater aquaculture and fishery products (t live weight equivalent) from 1996-2019. b) Percent of global marine and freshwater aquaculture and fishery production exported, excluding re-exports. c) Average number of export partners (out degree) by production method and environment. d) Number of countries comprising 75% of global exports by production method and environment with the global total in the black line.  e) Number of countries comprising 75% of global imports by production method and environment with the global total in the black line.](outputs/fig1.png)

@@

![Figure 2: Regional trade flows by production source (habitat and method). a) Total imports (positive) and exports (negative) colored by source, with net import trend in black. b) Bilateral flows colored by production source with exporting region along the rows and importing region along the columns. Values represent million tonnes in live weight equivalents. Note the scale difference across rows.](outputs/fig2.png)

@@

![Figure 3: Aquatic food apparent consumption (supply) trends and regional patterns. a) Global aquatic food apparent consumption by production source over time. b) Regional aquatic food apparent consumption by production source over time. c) Global aquatic food domestic versus foreign sourcing over time. d) Regional aquatic food domestic versus foreign sourcing over time. ](outputs/fig3.png)

>>>>

```{r load_data}
# Directory
datadir <- "qa/outputs_20240221"

@@

![Figure 1: Increases in global export of aquatic foods. a) Exports of global marine and freshwater aquaculture and fishery products (t live weight equivalent) from 1996-2019. b) Percent of global marine and freshwater aquaculture and fishery production exported, excluding re-exports. c) Average number of export partners (out degree) by production method and environment. d) Number of countries comprising 75% of global exports by production method and environment with the global total in the black line.  e) Number of countries comprising 75% of global imports by production method and environment with the global total in the black line.](qa/outputs_20240221/fig1.png)

@@

![Figure 2: Regional trade flows by production source (habitat and method). a) Total imports (positive) and exports (negative) colored by source, with net import trend in black. b) Bilateral flows colored by production source with exporting region along the rows and importing region along the columns. Values represent million tonnes in live weight equivalents. Note the scale difference across rows.](qa/outputs_20240221/fig2.png)

@@

![Figure 3: Aquatic food apparent consumption (supply) trends and regional patterns. a) Global aquatic food apparent consumption by production source over time. b) Regional aquatic food apparent consumption by production source over time. c) Global aquatic food domestic versus foreign sourcing over time. d) Regional aquatic food domestic versus foreign sourcing over time. ](qa/outputs_20240221/fig3.png)
